Modeling the impacts of replacing car trips with combined public transport and cycling: Reproducible methods, results and actionable evidence from the XXX project

### 2023-11-28 paper/PaperCEUS/PaperCEUS.tex
knit

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Modelling the impacts of replacing car trips with combined public transport and cycling: Reproducible methods, results and actionable evidence from the XXX project},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}

@@

  \title{Modelling the impacts of replacing car trips with combined
public transport and cycling: Reproducible methods, results and
actionable evidence from the XXX project}
    \author[CERIS]{Rosa Félix\corref{cor1}%
  \corref{cor1}%
  }
   \ead{rosamfelix@tecnico.ulisboa.pt} 
    \author[CERIS]{Filipe Moura%
  %
  }
   \ead{fmoura@tecnico.ulisboa.pt} 
    \author[ITS]{Robin Lovelace%
  %
  }
   \ead{r.lovelace@uleeds.uk} 
      \affiliation[CERIS]{CERIS, Instituto Superior Técnico -
Universidade de Lisboa, Av Rovisco Pais 1, 1049-001 Lisboa, Portugal}
    \affiliation[ITS]{Institute for Transport Studies, University of
Leeds. 34-40 University Rd, Leeds LS2 9JT, UK}
    \cortext[cor1]{Corresponding author}

@@

To achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively) (Presidência do
Conselho de Ministros, 2019), the Lisbon's Metropolitan Department of
Transport introduced \emph{XXX}\footnote{See https://xxx.xxx. \emph{For
  double blind peer-review process, the authors decided to truncate the
  name and references to this tool}.}, a decision support tool that
facilitates the planning, design, and development of a metropolitan
cycling network (ref X).

@@

\hypertarget{modelling-origin-destination-trips}{%
\subsection{Modelling Origin-Destination
trips}\label{modelling-origin-destination-trips}}

@@

\hypertarget{modelling-routes}{%
\subsection{Modelling routes}\label{modelling-routes}}

The mobility survey collects the origin and destination of trips but
does not include the respective routes. Modelling the realistic cycling
+ PT routes between OD pairs depends on assumptions regarding the
characteristics of the cycling and road networks and the location of
public transport interfaces. Other constraints regarding the behavior of
potential cyclists determine the routing results. For example, such
restrictions can favor low speed, low traffic streets, more direct
routes, and less steep paths, among others, which are suitable for
cycling.

@@

\hypertarget{modelling-intermodality}{%
\subsection{Modelling intermodality}\label{modelling-intermodality}}

@@

The conversion of avoided emissions into avoided welfare loss and
respective monetary valuation was based on the EU Guide to Cost-benefit
Analysis (Sartori et al., 2014) and the best up-to-date reference values
for the various gases (Bickel et al., 2006; Nash et al., 2003; Sartori
et al., 2014): 8.44 €/ton for CO, 2,867.85 €/ton for
NO\textsubscript{X}, 340,969.27 €/ton for PM10, 7,169.62 €/ton for VOC
and 35.85 €/ton for CO\textsubscript{2}eq. The social impacts are in
avoided premature mortality. This result is finally monetized using the
\emph{Statistical Value of Life} for Portugal: €3,055,358/fatality
(Silva et al., 2021). We updated all the monetary reference values of
the literature based on the annual inflation rate in Portugal for
2022\footnote{See
  \href{https://www.ine.pt/xportal/xmain?xpid=INE\&xpgid=ipc}{Statistics
  Portugal tool for inflation rate estimates between years}.}, and our
10-years estimations assumed a discount rate of 5\% and inflation of
3\%.

>>>>

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Modeling the impacts of replacing car trips with combined public transport and cycling: Reproducible methods, results and actionable evidence from the XXX project},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}

@@

  \title{Modeling the impacts of replacing car trips with combined
public transport and cycling: Reproducible methods, results and
actionable evidence from the XXX project}
    \author[CERIS]{Rosa Félix\corref{cor1}%
  \corref{cor1}%
  }
   \ead{rosamfelix@tecnico.ulisboa.pt} 
    \author[CERIS]{Filipe Moura%
  %
  }
   \ead{fmoura@tecnico.ulisboa.pt} 
    \author[ITS]{Robin Lovelace%
  %
  }
   \ead{r.lovelace@uleeds.uk} 
      \affiliation[CERIS]{CERIS, Instituto Superior Técnico -
Universidade de Lisboa, Av Rovisco Pais 1, 1049-001 Lisboa, Portugal}
    \affiliation[ITS]{Institute for Transport Studies, University of
Leeds. 34-40 University Rd, Leeds LS2 9JT, UK}
    \cortext[cor1]{Corresponding author}

@@

To achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively) (Presidência do
Conselho de Ministros, 2019), the Lisbon's Metropolitan Department of
Transport introduced \emph{XXX}\footnote{See xxx.xxx. \emph{For double
  blind peer-review process, the authors decided to truncate the name
  and references to this tool}.}, a decision support tool that
facilitates the planning, design, and development of a metropolitan
cycling network (ref X).

@@

\hypertarget{modeling-origin-destination-trips}{%
\subsection{Modeling Origin-Destination
trips}\label{modeling-origin-destination-trips}}

@@

\hypertarget{modeling-routes}{%
\subsection{Modeling routes}\label{modeling-routes}}

The mobility survey collects the origin and destination of trips but
does not include the respective routes. Modeling the realistic cycling +
PT routes between OD pairs depends on assumptions regarding the
characteristics of the cycling and road networks and the location of
public transport interfaces. Other constraints regarding the behavior of
potential cyclists determine the routing results. For example, such
restrictions can favor low speed, low traffic streets, more direct
routes, and less steep paths, among others, which are suitable for
cycling.

@@

\hypertarget{modeling-intermodality}{%
\subsection{Modeling intermodality}\label{modeling-intermodality}}

@@

The conversion of avoided emissions into avoided welfare loss and
respective monetary valuation was based on the EU Guide to Cost-benefit
Analysis (Sartori et al., 2014) and the best up-to-date reference values
for the various gases (Bickel et al., 2006; Nash et al., 2003; Sartori
et al., 2014): 8.44 €/ton for CO, 2,867.85 €/ton for
NO\textsubscript{X}, 340,969.27 €/ton for PM10, 7,169.62 €/ton for VOC
and 35.85 €/ton for CO\textsubscript{2}eq. The social impacts are in
avoided premature mortality. This result is finally monetized using the
\emph{Statistical Value of Life} for Portugal: €3,055,358/fatality
(Silva et al., 2021). We updated all the monetary reference values of
the literature based on the annual inflation rate in Portugal for
2022\footnote{See
  \href{https://www.ine.pt/xportal/xmain?xpid=INE\&xpgid=ipc}{Statistics
  Portugal tool for inflation rate estimates between years}.}, and our
10-years estimations assumed a discount rate of 5\% and inflation of
3\%. See \protect\hyperlink{research-data}{Research Data} for all the
input values we used.
